---
title: "Grammar of Graphics"
author: "Amit Kapoor"
date: "13 July 2015"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)

library(grid)
library(ggplot2)
library(gridExtra)

theme_black <- function(base_size = 16, base_family = "Helvetica") {
    theme(
    line =  element_line(colour = "black", size = 0.5, linetype = 1,
                            lineend = "butt"),
    rect =  element_rect(fill = "white", colour = "black", size = 0.5, linetype = 1),
    text =  element_text(family = base_family, face = "plain",
                  colour = "black", size = base_size,
                  hjust = 0.5, vjust = 0.5, angle = 0, lineheight = 0.9),
    
    axis.text =          element_text(size = rel(0.8), colour = "grey70"),
    strip.text =         element_text(size = rel(0.8), colour = "grey70"),

    axis.line =          element_line(colour = "grey70"),
    axis.text.x =        element_text(vjust = 1),
    axis.text.y =        element_text(hjust = 1),
    axis.ticks =         element_line(colour = "grey70", size = 0.2),
    axis.title =         element_text(colour = "grey70"),
    axis.title.x =       element_blank(),
    axis.title.y =       element_blank(),
  # axis.title.x =       element_text(vjust = 1),
  # axis.title.y =       element_text(angle = 90),
    axis.ticks.length =  unit(0.3, "lines"),
    axis.ticks.margin =  unit(0.5, "lines"),

    legend.background =  element_rect(fill = 'black'),
    legend.margin =      unit(0.2, "cm"),
    legend.key =         element_rect(fill = "grey20", colour = "grey50"),
    legend.key.size =    unit(1.2, "lines"),
    legend.key.height =  NULL,
    legend.key.width =   NULL,
    legend.text =        element_text(size = rel(0.8), colour = "grey50"),
    legend.text.align =  NULL,
    legend.title =       element_text(size = rel(0.8), face = "plain", hjust = 0, colour = "grey50"),
    legend.title.align = NULL,
    legend.position =    "none",
    legend.direction =   "vertical",
    legend.justification = "center",
    legend.box =         NULL,

    panel.background =   element_rect(fill = "black", colour = NA),
    panel.border =       element_rect(fill = NA, colour = NA),
    panel.grid.major =   element_line(colour = "grey50", size = 0.2),
    panel.grid.minor =   element_line(colour = "black", size = 0.5),
    panel.margin =       unit(0.25, "lines"),

    strip.background =   element_rect(fill = "grey30", colour = "grey10"),
    strip.text.x =       element_text(),
    strip.text.y =       element_text(angle = -90),

    plot.background =    element_rect(colour = "black", fill = "black"),
    plot.title =         element_text(size = rel(1.2)),
    plot.margin =        unit(c(1, 1, 0.5, 0.5), "lines"),

    complete = TRUE
  )
}
attr(theme_black(), "complete")

```


Load the Humble Data
```{r, echo=FALSE}
areas <- c("N", "E", "W", "S", "C")
sales <- c(5, 25, 15, 20, 10)
profit <- c(2, 8, 6, 5, 3)
humble <- data.frame(areas, sales, profit)
humble$areas <-ordered(humble$areas, levels=c("N", "E", "W", "S", "C"))
humble
humble.base <-humble

# For maps
lat <- c(0, 1, -1, 0, 0)
long <- c(1, 0, 0, -1, 0)
humble.map <- data.frame(areas, sales, profit, lat, long)


# For the Waterfall Chart
humble$id <- seq_along(humble$areas)
humble$end_sales <- cumsum(humble$sales)
humble$start_sales <- c(0, head(humble$end_sales, -1))
humble$end_profit <- cumsum(humble$sales)
humble$start_profit <- c(0, head(humble$end_profit, -1))
humble

ggplot(humble, aes(x = "", fill = areas, weight = sales)) +
  geom_bar(width = 1)  + coord_polar("y") 


```

Point - Cartesian (pc)
```{r humble-point, echo=FALSE}
pc <- ggplot(humble, aes(areas,sales, color = areas)) +
  geom_point(size = 6) +
  ylim(0, 25) +
  theme_black()
pc
```

Line - Cartesian (lc)
```{r humble-line, echo=FALSE}
lc <- ggplot(humble, aes(areas, weight = sales, fill = areas)) +
  geom_bar(width = 0.1)  +
  theme_black()
lc
```

Bar - Cartesian (bc)
```{r humble-bar, echo=FALSE}
bc <- ggplot(humble, aes(areas, weight = sales, fill = areas)) +
  geom_bar()  +
  theme_black()
bc
```

Bar Stacked - Cartesian (sc)
```{r humble-bar-stacked, echo=FALSE}
sc <- ggplot(humble, aes(x = "", fill = areas, weight = sales)) +
  geom_bar(width = 0.3)  + xlab("") +
  theme_black()
sc
```

Bar Waterfall - Cartesian (wc)
``` {r humble-bar-waterfall, echo=FALSE}
wc <- ggplot(humble, aes(areas, fill = areas)) + geom_rect(aes(x = areas,
   xmin = id - 0.5, xmax = id + 0.5, ymin = end_sales, 
   ymax = start_sales)) +
   theme_black()
wc
```

Point - Cartesian Flip (pf)
```{r humble-point-flip, echo=FALSE}
pf <- pc + coord_flip()
pf
```

Line - Cartesian Flip (lf)
```{r humble-line-flip, echo=FALSE}
lf <- lc + coord_flip()
lf
```

Bar - Cartesian Flip (bf)
```{r humble-bar-flip, echo=FALSE}
bf <- bc + coord_flip()
bf
```

Bar Stacked - Cartesian Flip (sf)
```{r humble-bar-stacked-flip, echo=FALSE}
sf <- sc + geom_bar(width = 0.3) + coord_flip()
sf
```

Bar Waterfall - Cartesian Flip (wf)
``` {r humble-bar-waterfall-flip, echo=FALSE}
wf <- wc + coord_flip()
wf
```

Point - Polar - x (ppx)
```{r humble-point-polar-x, echo=FALSE}
ppx <- pc + coord_polar(theta = "x")
ppx
```

Line - Polar -x (lpx)
```{r humble-line-polar-x, echo=FALSE}
lpx <- lc + coord_polar(theta ="x")
lpx
```

Bar - Polar - x (bpx)
```{r humble-bar-polar-x, echo=FALSE}
bpx <- bc + geom_bar(width=1) + coord_polar(theta ="x")
bpx
```

Bar Stacked - Polar - x (spx)
```{r humble-bar-stacked-polar-x, echo=FALSE}
spx <- sc + geom_bar(width = 1) + coord_polar(theta ="x")
spx
```

Bar Waterfall - Polar - x (wpx)
``` {r humble-bar-waterfall-polar-x, echo=FALSE}
wpx <- wc + coord_polar(theta ="x")
wpx
```

Point - Polar - y (ppy)
```{r humble-point-polar-y, echo=FALSE}
ppy <- pc + coord_polar(theta ="y")
ppy
```

Line - Polar -y (lpy)
```{r humble-line-polar-y, echo=FALSE}
lpy <- lc + coord_polar(theta ="y")
lpy
```

Bar - Polar - y (bpy)
```{r humble-bar-polar-y, echo=FALSE}
bpy <- bc + geom_bar(width=1) + coord_polar(theta ="y")
bpy
```

Bar Stacked - Polar - y (spy)
```{r humble-bar-stacked-polar-y, echo=FALSE}
spy <- sc + geom_bar(width = 1) + coord_polar(theta ="y")
spy
```

Bar Waterfall - Polar - y (wpy)
``` {r humble-bar-waterfall-polar-y, echo=FALSE}
wpy <- wc + coord_polar(theta ="y")
wpy
```


Plot - Grid  
```{r humble-plots, echo=FALSE}

humble_plots_cart <- arrangeGrob(pc, lc, bc, sc, wc,
                              ncol=3, nrow =2)
humble_plots_cart
ggsave(humble_plots_cart, file="img/humble_plots_cart.png",
       width = 16, height = 8.5 )

humble_plots_flip <- arrangeGrob(pf, lf, bf, sf, wf,
                                 ncol=3, nrow =2)
humble_plots_flip
ggsave(humble_plots_flip, file="img/humble_plots_flip.png",
       width = 16, height = 8.5 )

humble_plots_polar_x <- arrangeGrob(ppx, lpx, bpx, spx, wpx,
                       ncol=3, nrow =2)
humble_plots_polar_x
ggsave(humble_plots_polar_x, file="img/humble_plots_polar_x.png",
       width = 16, height = 8.5 )

humble_plots_polar_y <- arrangeGrob(ppy, lpy, bpy, spy, wpy,
                       ncol=3, nrow =2)
humble_plots_polar_y
ggsave(humble_plots_polar_y, file="img/humble_plots_polar_y.png",
       width = 16, height = 8.5 )
```


