---
title: "Pindecode"
author: "Amit Kapoor"
date: "13 July 2015"
output: html_document
---

Pindecode Map

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)

library(grid)
library(ggplot2)
library(gridExtra)
  
theme_black_map <- function(base_size = 16, base_family = "Helvetica") {
    theme(
    line =  element_line(colour = "black", size = 0.5, linetype = 1,
                            lineend = "butt"),
    rect =  element_rect(fill = "white", colour = "black", size = 0.5, linetype = 1),
    text =  element_text(family = base_family, face = "plain",
                  colour = "black", size = base_size,
                  hjust = 0.5, vjust = 0.5, angle = 0, lineheight = 0.9),
    
    axis.text =          NULL,
    strip.text =         element_text(size = rel(0.8), colour = "grey70"),

    axis.line =          element_blank(),
    axis.text.x =        element_text(vjust = 1),
    axis.text.y =        element_text(hjust = 1),
    axis.ticks =         element_line(colour = "grey20", size = 0.2),
    axis.title =         element_text(colour = "grey20"),
    axis.title.x =       element_blank(),
    axis.title.y =       element_blank(),
    axis.ticks.length =  unit(0.3, "lines"),
    axis.ticks.margin =  unit(0.2, "lines"),

    legend.background =  element_rect(fill = 'black'),
    legend.margin =      unit(0.2, "cm"),
    legend.key =         element_rect(fill = "grey20", colour = "grey50"),
    legend.key.size =    unit(1.2, "lines"),
    legend.key.height =  NULL,
    legend.key.width =   NULL,
    legend.text =        element_text(size = rel(0.8), colour = "grey50"),
    legend.text.align =  NULL,
    legend.title =       element_text(size = rel(0.8), face = "plain", hjust = 0, colour = "grey50"),
    legend.title.align = NULL,
    legend.position =    "none",
    legend.direction =   "vertical",
    legend.justification = "center",
    legend.box =         NULL,

    panel.background =   element_rect(fill = "black", colour = NA),
    panel.border =       element_rect(fill = NA, colour = NA),
    panel.grid.major =   element_line(colour = "grey20", size = 0.2),
    panel.grid.minor =   element_line(colour = "black", size = 0.5),
    panel.margin =       unit(0.25, "lines"),

    strip.background =   element_rect(fill = "grey40", colour = "grey10"),
    strip.text.x =       element_text(),
    strip.text.y =       element_text(angle = -90),

    plot.background =    element_rect(colour = "black", fill = "black"),
    plot.title =         element_text(size = rel(1.2)),
    plot.margin =        unit(c(0.5, 0.5, 0.5, 0.5), "lines"),

    complete = TRUE
  )
}
attr(theme_black_map(), "complete")

```

Load the data
```{r}
df <- read.csv("data/pincode.csv")

```

Lets create the pincode map
```{r}
pinmapAll <- ggplot(df) + aes(lat,lon) + 
  geom_point(color = "orange", alpha = 0.3, size = 1.5) +
  coord_equal() + theme_black_map()
pinmapAll
```

Lets create the pincode map for each unique pincode only
```{r}
library(dplyr)
dfUniquePin <- df %>%
             group_by(pincode, lat, lon) %>%
             tally() %>%
             ungroup()

par(bg = "black")
pinmapUnique <- ggplot(dfUniquePin) + aes(lat,lon) + 
  geom_point(color = "orange", alpha = 0.3, size = 1.5) +
  coord_equal() + theme_black_map()
pinmapUnique

ggsave("img/pinmapUnique.png", pinmapUnique, width = 8.4, height = 9)
```

Lets create the pincode map for each unique starter state
```{r}
# Add Code Market
dfUniquePin <- dfUniquePin %>% 
               mutate(start = trunc(pincode / 100000))

dfUniquePin$start <-  as.factor(dfUniquePin$start)
str(dfUniquePin)

pinmapUniqueStart <- ggplot(dfUniquePin) + aes(lat,lon, color = start) + 
  geom_point(alpha = 0.3, size = 1.5) +
  coord_equal() + theme_black_map()
pinmapUniqueStart

ggsave("img/pinmapUniqueStart.png", pinmapUniqueStart, 
       width = 8.4, height = 9)
```

Color them using Saturation
```{r}
# Add Code Market

pinmapUniqueStartSat <- ggplot(dfUniquePin) + 
  aes(lat,lon, color = start) + 
  scale_color_brewer("start", palette = "Reds") +
  geom_point(alpha = 0.3, size = 1.5) +
  coord_equal() + theme_black_map()
pinmapUniqueStartSat

ggsave("img/pinmapUniqueStartSat.png", pinmapUniqueStartSat, 
       width = 8.4, height = 9)
```


Create Chloroplethe
``` {r map-choro}
library(choroplethr)
str(df_state_demographics)

library(maps)
map("state")
states <- map_data("state")
choro <- merge(states, df_state_demographics, sort = FALSE, by = "region")

choroBad <- ggplot(choro) + 
  aes(long, lat, group = group, fill = region) +
  geom_polygon(linetype = 2, linewidth = 10, color = "black") + 
  coord_map() + theme_black() + 
  theme ( legend.position = "none",
         axis.line = element_blank() 
         )
choroBad

choroBad <- ggplot(choro) + 
  aes(long, lat, group = group, fill = region) +
  geom_polygon(linewidth = 12, color = "grey") + 
  coord_map() + theme_black() + 
  scale_fill_brewer("region", palette = "Set1") +
  theme ( legend.position = "right",
         axis.line = element_blank() 
         )
choroBad

ggsave(choroBad, "img/choroBad"), 
       width = 16, height = 9)

