---
title: "5-MultiViz"
author: "Amit Kapoor"
date: "15 July 2015"
output: html_document
---

We will use the diamonds dataset to make the visualization

```{r}
knitr::opts_chunk$set(cache=TRUE)

library(grid)
library(ggplot2)
library(gridExtra)

theme_multi <- function(base_size = 24, base_family = "Helvetica") {
    theme(
    line =  element_line(colour = "black", size = 0.5, linetype = 1,
                            lineend = "butt"),
    rect =  element_rect(fill = "white", colour = "black", size = 0.5, linetype = 1),
    text =  element_text(family = base_family, face = "plain",
                  colour = "black", size = base_size,
                  hjust = 0.5, vjust = 0.5, angle = 0, lineheight = 0.9),
    
    axis.text =          element_text(size = rel(0.8), colour = "grey60"),
    strip.text =         element_text(size = rel(0.8), colour = "grey80"),

    axis.line =          element_line(colour = "grey80"),
    axis.text.x =        element_text(vjust = 1),
    axis.text.y =        element_text(hjust = 1),
    axis.ticks =         element_line(colour = "grey50", size = 0.2),
    axis.title =         element_text(colour = "grey80"),
    axis.title.x =       element_text(vjust = 1),
    axis.title.y =       element_text(angle = 90),
    axis.ticks.length =  unit(0.3, "lines"),
    axis.ticks.margin =  unit(0.5, "lines"),

    legend.background =  element_rect(fill = "black"),
    legend.margin =      unit(0.4, "cm"),
    legend.key =         element_rect(fill = "grey20", colour = "grey50"),
    legend.key.size =    unit(2, "lines"),
    legend.key.height =  unit(0.8, "cm"),
    legend.key.width =   unit(0.8, "cm"),
    legend.text =        element_text(size = rel(0.8), colour = "grey50"),
    legend.text.align =  NULL,
    legend.title =       element_text(size = rel(1.0), face = "plain", 
                                      hjust = 2, colour = "grey70"),
    legend.title.align = NULL,
    legend.position =    "right",
    legend.direction =   "vertical",
    legend.justification = "center",
    legend.box =         NULL,

    panel.background =   element_rect(fill = "black", colour = NA),
    panel.border =       element_rect(fill = NA, colour = NA),
    panel.grid.major =   element_line(colour = "grey40", size = 0.2),
    panel.grid.minor =   element_line(colour = "black", size = 0.5),
    panel.margin =       unit(0.25, "lines"),

    strip.background =   element_rect(fill = "grey30", colour = "grey10"),
    strip.text.x =       element_text(),
    strip.text.y =       element_text(angle = -90),

    plot.background =    element_rect(colour = "black", fill = "black"),
    plot.title =         element_text(size = rel(1.2)),
    plot.margin =        unit(c(1, 1, 0.5, 0.5), "lines"),

    complete = TRUE
  )
}
attr(theme_multi(), "complete")

```

Create three dataset - all, sample of 5000 and sample 1000

```{r}
library(dplyr)
data(diamonds)
dlarge <- sample_n(diamonds, 2500)
dsmall <- sample_n(diamonds, 500)
```

Start with two dimension viz - price vs carat

```{r}
d2 <- ggplot(diamonds) + aes(carat,price) + 
  geom_point(color = "orange", alpha = 0.4, size = 2) +
  theme_multi()
d2 
ggsave("img/d2.png", d2, width = 16, height = 9)
```


Lets do a log transform on the axis

```{r}
d2log <- ggplot(diamonds) + aes(log10(carat), log10(price)) + 
  geom_point(color = "orange", alpha = 0.4, size = 2) +
  theme_multi()
d2log 
ggsave("img/d2log.png", d2log, width = 16, height = 9)
```


Lets subset the data

```{r}
d2logSubset <- ggplot(diamonds) + aes(log10(carat), log10(price)) + 
  geom_point(color = "orange", alpha = 0.4, size = 2) +
  ylim(c(4.0,4.3)) + xlim(c(0,0.8)) +
  theme_multi()
d2logSubset 
ggsave("img/d2logSubset.png", d2logSubset, width = 16, height = 9)
```


Three dimension viz - Shape (Nominal)

```{r}
d3ShapeN <- ggplot(dlarge) + aes(log10(carat), log10(price), shape = cut) + 
  geom_point(alpha = 0.4, size = 4, color = "orange") +
  theme_multi()
d3ShapeN
ggsave("img/d3ShapeN.png", d3ShapeN, width = 16, height = 9)
```

Three dimension viz - Colour (Nominal)

```{r}
d3ColorN <- ggplot(diamonds) + aes(log10(carat), log10(price), 
                                   color = color) + 
  geom_point(alpha = 0.4, size = 2) +
  theme_multi()
d3ColorN
ggsave("img/d3ColorN.png", d3ColorN, width = 16, height = 9)
```

Three dimension viz - Size (Quantiative)

```{r}
d3SizeQ <- ggplot(diamonds) + aes(log10(carat), log10(price), 
                                  size = log(x*y*z)) + 
  geom_point(alpha = 0.4, color = "orange") + 
  theme_multi()
d3SizeQ
ggsave("img/d3SizeQ.png", d3SizeQ, width = 16, height = 9)
```


Three dimension viz - Static 3d (Does not work!)

```{r}
library(scatterplot3d)

# Get the scales for color
library(scales)
cutColor <- alpha(as.numeric(diamonds$cut), 0.3)

# Create the dummy plot
scatterplot3d(x = log10(diamonds$carat), z = log10(diamonds$price), 
              y = diamonds$cut)

# Cover it up with black              
par(bg="black")
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "black")

# Create the actual plot
scatterplot3d(x = log10(diamonds$carat), z = log10(diamonds$price), 
              y = diamonds$cut, color = cutColor,
              xlab = "log10(carat)", zlab = "log10(price)", ylab = "cut",
              bg = "black", col.axis = "grey60", col.grid = "grey80",
              col.lab ="grey80")
```


Three dimension viz - Interactive 3d

```{r}
library(rgl)
rgl.open()    # Open a new RGL device

rgl.bg(color = "black") # Setup the background color
rgl.viewpoint(theta = 15, phi = 20, zoom = 1)

library(scales)
cutColor <- alpha(as.numeric(diamonds$cut), 0.3)

plot3d(log10(diamonds$carat), log10(diamonds$price), diamonds$cut, 
       size = 2, type = "p", col = cutColor, add = TRUE)
decorate3d(xlab = "log10(carat)", ylab="log10(price)", zlab="cut",
       col.axis = "grey20", col.grid = "grey20", col.lab ="grey20",
       top = TRUE, box = TRUE, aspect = c(16,9,7))       

movie3d(spin3d(axis = c(0,1,0), rpm = 5), duration=6, 
        dir = getwd(), type = "gif")

rgl.close()

```



Four dimension viz - Colour + Size

```{r}
d4ColorSize <- ggplot(diamonds) + aes(log10(carat), log10(price), 
                                    color = color, size = x) + 
  geom_point(alpha = 0.4) + scale_size(range = c(1, 5)) +
  theme_multi()
d4ColorSize
ggsave("img/d4ColorSize.png", d4ColorSize, width = 16, height = 9)

```


Four dimension viz - Colour + Facet - 1d
```{r}
d4ColorFacet <- ggplot(dlarge) + aes(log10(carat), log10(price), 
                                    color = color) + 
  geom_point(alpha = 0.5, size = 2) + facet_grid(. ~ color) +
  theme_multi()
d4ColorFacet
ggsave("img/d4ColorFacet.png", d4ColorFacet, width = 16, height = 9)
```


Five dimension viz - Colour + Facet - 2d
```{r}
d5ColorFacet <- ggplot(dlarge) + aes(log10(carat), log10(price), 
                                    color = color) + 
  geom_point(alpha = 0.5, size = 2) + facet_grid(cut ~ color) +
  theme_multi()
d5ColorFacet
ggsave("img/d5ColorFacet.png", d5ColorFacet, width = 16, height = 9)
```

Five dimension viz - Matrix
```{r}
library(GGally)
dSelect <- diamonds %>%
           select(log10(price), log10(carat), cut)
ggpairs(dSelect)
```


Five dimensions viz - Subplot (Not Working)
```{r}
library(ggsubplot)

ggplot(diamonds) + aes(carat, price) + geom_point(size = 0) +
  geom_subplot2d(aes(carat, price, 
                     subplot = geom_bar(aes(color, fill = color), 
                                        position = "dodge")), 
                 bins = c(10, 14), y_scale = free,
                 height.adjust = 0.8, width.adjust = 0.8,
                 ref = ref_box(aes(color = length(color)))) +
  scale_color_gradient("Total\ncount", low = "grey70",
                       high = "black")                       

```

Six dimension plus - Parallel Coordinates
```{r}
library(GGally)
ggparcoord(data = iris, columns = 1:4, groupColumn = 5, 
           order = "anyClass") + theme_multi()
```


Six dimension plus - TablePlot
```{r}
library(tabplot)
tab <- tableplot(diamonds, sortCol = price, 
                 select = c(price, carat, cut, color, clarity, x, y, z,
                            depth, table))
tableSave(tab, filename = "tableplot.png", width = 16, height = 9,
           fontsize = 16, legend.lines = 8)

# Zooming & Filtering
tabZoom <- tableplot(diamonds, 
                     select = c(price, carat, cut, color, clarity), 
                     sortCol = price, from = 0, to = 5)
                    
tableSave(tabZoom, filename = "tableplotzoom.png", width = 16, height = 9,
           fontsize = 16, legend.lines = 8)

```


Star Coordinates


```{r}
d <- dlarge
d$log10price <- log10(d$price)
d$log10carat <- log10(d$carat)

d <- subset(d, select=c(log10price, log10carat, color, cut, clarity))

# Convert factors to 
d$cut <- as.numeric(x$cut)
d$color <- as.numeric(x$color)
d$clarity <- as.numeric(x$clarity)


# Refer to following post
# http://stats.stackexchange.com/questions/58001/how-to-plot-a-5d-data-set-in-star-coordinates

# Normalize the data
d.range <- apply(d, 2, range)
z <- t((t(d) - d.range[1,]) / (d.range[2,] - d.range[1,]))

dm <- dim(z)[2] # Dimensions
prj <- t(sapply((1:dm)/dm, function(i) c(cos(2*pi*i), sin(2*pi*i))))
star <- z %*% prj

library(scales)
cols <- alpha(x$cut, 0.5)

par(bg="black")
plot(rbind(apply(star, 2, range), apply(prj*1.25, 2, range)), 
     type="n", bty="n", xaxt="n", yaxt="n",
     main="Star Coordinates", xlab="", ylab="")

tmp <- apply(prj, 1, function(v) lines(rbind(c(0,0), v), col = "white"))
points(star, pch=19, col=cols, cex = 1)
text(prj * 1.2, labels=colnames(z), cex=1.5, col="white")

# png("img/starcoord.png", width = 800, height = 450, units= "px")	

```

# Star plot 

```{r}

par(bg = "black")

dstar <- dsmall[1:100,]

# Create the x,y coordinate plot
dstar$log10carat <- log10(dstar$carat)
dstar$log10price <- log10(dstar$price)
loc <- data.matrix(dstar[,11:12])

plot(loc, col.axis = "white", col.grid = "white")

palette(rainbow(12, s = 0.6, v = 0.75, alpha = 0.7))

stars(dstar[,2:6], key.loc = c(-1, 3), scale = TRUE, 
      locations = loc, axes = TRUE, len =0.07, radius = TRUE,
      full = TRUE, labels = NULL,  draw.segments = TRUE,
      xlab="log10(carat)", ylab="log10price", frame.plot = FALSE,
      col.axis = "grey80", col.grid = "grey80", col.lab ="grey80", 
      xlim=c(-0.7,0.7))

stars(dstar[,2:6], key.loc = c(-2, 10), scale = TRUE, 
      locations = NULL, len =1, radius = TRUE,
      full = TRUE, labels = NULL,  draw.segments = TRUE)


```


Bertin's Matrix (Don't do for the diamonds set)
```{r}
install.packages("bertin",repos="http://r-forge.r-project.org")
library(bertin)

data(Hotel)
image.bertin(bertinrank(Hotel), main= "Hotel data")
plot.bertin(bertinrank(Hotel), main= "Hotel data")
plot.bertin(Hotel, palette=c("white","black"))

```